Malacology: A Programmable Storage System

### 2016-10-18 paper/paper.tex
updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

Ceph also addresses the challenge of balancing metadata load with a separate
metadata cluster. This cluster uses load balancing policies to migrate
directory inodes around the cluster to alleviate load. The policies use metrics
based on system state (e.g.  CPU and memory utilization) and statistics
collected by the cluster (e.g. the popularity of an inode). Ceph uses dynamic
subtree partitioning to move variable sized namespace subtrees. These units can
be shipped anywhere (i.e., to any metadata server of any capacity) at any time
for any reason. The original balancer was designed with hard-coded policies and
tunables.

@@

{\bf Shared Resource Interface.} The metadata service also manages sessions
with its clients. This gives both subsystems (metadata servers and clients) the
ability to cache data and obtain locks. The metadata service is responsible for
responding to client requests for capabilities by first revoking caps from
other clients.  Currently, clients voluntarily release their capabilities, and
the metadata server maintains a queue of requests.  Both clients and metadata
servers use a best-effort approach to revoking or releasing capabilities.

The clients retain the best-effort, voluntary release of capabilities, but in
Malacology, the queuing policies are generalized within the MDS to allow for
centralized policies such as fairness or priority.

{\bf Load balancing.} Mantle~\cite{sevilla:sc15-mantle}, a programmable
metadata load balancer, has been implemented on Malacology so that its
infrastructure can enjoy all the properties of existing internal abstractions.
The load balancing logic is intact but the infrastructure has been improved to
safely load, manage, and persist its load balancing policies.  Composing Mantle
using the service metadata, durability and beacon interfaces, Mantle can safely
version balancer policies, save balancer policies in the back end object store
and centralize warnings/errors.

>>>>

Ceph also addresses the challenge of balancing metadata load with a separate
metadata cluster. This cluster uses load balancing policies to migrate
directory inodes around the cluster to alleviate overload at single nodes. The policies use metrics
based on system state (e.g.  CPU and memory utilization) and statistics
collected by the cluster (e.g. the popularity of an inode). Ceph uses dynamic
subtree partitioning to move variable sized namespace
subtrees~\cite{weil:sc2004-dyn-metadata}. These units can
be shipped anywhere (i.e., to any metadata server of any capacity) at any time
for any reason. The original balancer was designed with hard-coded policies and
tunables.

@@

{\bf Shared resource interface.}
The metadata service manages client sessions, allowing clients to obtain locks
(e.g. file byte ranges), and capabilities (e.g. to cache file data). Clients
and metadata servers use a cooperative protocol in which clients voluntarily
release resources back to the metadata service in order to implement sharing
policies. While the current policy for sharing access and voluntarily
releasing resources is largely best-effort, Malacology supports generalized
policies between metadata servers and clients that can be used to implement 
fairness or priority.

{\bf Load balancing.} Mantle~\cite{sevilla:sc15-mantle}, a programmable
metadata load balancer, has been implemented on Malacology so that its
infrastructure can enjoy all the properties of existing internal abstractions.
The load balancing logic is intact but the infrastructure has been improved to
safely load, manage, and persist its load balancing policies.  Composing Mantle
using the service metadata and durability interfaces, Mantle can safely
version balancer policies, save balancer policies in the backend object store
and centralize warnings/errors.
